Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-09 paper.tex
Cambios locales

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of how
many books should be printed for delivery to bookstores; printing too
many is the main issue, since it implies a loss of investment due to
inventory excess, but printing too few will also have a negative economic impact. In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores. A real dataset including the complete sales data for books published in Spain across several years has been used.
We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods has been applied to create forecasting models for book sales. 
The obtained models are able to predict sales from pre-publication data with
remarkable accuracy, and can be visualised as simple decision trees. Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book. 
This is also shown in the paper by addressing four example cases of representative publishers, regarding their number of sales and the number of different books they sell.
\end{abstract}

@@

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution, and storage processes; most of these costs are associated
with the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that there is an unknown
author or a new topic with no track record. Sales forecasts can
only be based on the knowledge obtained from other similar products,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, doing accurate
estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
Indeed,several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

Specifically, time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
is perhaps the most used technique to tackle sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this paper.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge of industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions, or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?
% (Paloma) Agree with Fergu, I don't think we should say this... Please review it.

% [pedro] La cosa es que esta gente toma libros ya publicados y de los que tienen todos los datos de ventas para analizar y obtener patrones de ventas. Nosotros trabajamos con datos de libros que ni siquiera se han impreso aún, por lo que no tenemos ni idea de cómo van a funcionar. Esta gente dispone de datos de ventas, mientras que nosotros sólo vamos a tener datos relativos a "¿dónde lo vas a poner a la venta?" o "¿vas a dar algún regalo para intentar vender más?" (cosas así).

@@

In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
% Antonio - Maybe we should describe them briefly...
%
In the same line, Thomassey et al. \cite{SThomassey2014} proposed using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
a very similar issue to the new book publishing one. % (Paloma) Very similar? Why?
The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
forecasting method based on extreme machine learning with adaptive metrics of inputs.
% Antonio - of -> as???
% (Paloma) It's "of" in the title...
The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
% Antonio - ver si está bien el cambio 'large number' -> 'majority'
and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
%FERGU: completar con: "In our case, these ideas ..."

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors did in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again? - JJ
                   % No, above we said that the efficiency depends on the field 
                   % of application and the available problem data. - pedro
A similar method is described by Chern et al. \cite{ChernWSF15}, who analysed 
historical data throughout online reviews, reviewer characteristics, and review 
influences to understand how electronic `word-of-mouth' influences product sales. 
The proposed method is suitable for those sales forecasting problems 
with a big amount of online reviews and historical data.

@@

The main objective of this paper is to forecast sales for 
%FERGU: el objetivo es la herramienta o la predicción?
unpublished books for which no historical data are available. Instead, just some
%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
descriptive and variables are known in advance related to the new book. In
order to do that, we have used a training dataset which includes
historical sales data % (Paloma) so, have we or have we not historical data? It's all contradictory
 for a big amount of books published in Spain for
several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends, or 
promotions, that classical prediction methods can not deal with. %FERGU: por qué?
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it in his or her own prediction process.

@@

First, after the publishing company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. % (Paloma) Why remove those with null values and not to use an algorithm to fill those missing values?
Furthermore, the initial set of variables, presented
in Table \ref{tabla:paramsOrig50}, has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}. % (Paloma) Where are they? In table 2?

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
Then, a Feature Selection (FS) process \cite{kittler1986feature} has
been carried out, as it is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}. The aim of these
% Did you know there were noisy features? Why? 
% You should include in the previous section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ 
algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem. 
  In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases of publishing companies in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these can be used as a decision-aid tool for the experts who have to decide on the best print-run quantity for new books to be published, in order to either maximise the benefit, or minimise the costs.

@@

In general, historical data are used to make time series, as well as for extracting common patterns and obtaining accurate predictions from them.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem. %PABLO: pre-sales data is mentioned briefly in introduction, expand it

Due to this situation, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e. those whose value do not depend on the book sales. Therefore, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. The third column shows
  the names of the variables used in the applied methods, and the last one indicates if they have been used as an input (independent) or an output (dependent) variable.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  publisher + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. On the other hand, \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher. In addition, this variable could be interesting to be used to test the prediction model, once it is built. Hence, the publisher could try different values for it and see what the predictor yields, in order to take the best decision.
%Pablo: still waiting the definition of the variables

@@

With regard to the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
% Antonio - Think about this... should we mention this?
% (Paloma) If you finally leave it, please review it because this last sentence is a bit confusing

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \cite{wiki:dewey}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

@@

Preprocessing a dataset means that it is revised in order to reduce errors, such as wrong or duplicated patterns, or for completing missing values. The aim is to look for the correctness,
homogeneity, and completeness of the data. % useless paragraph - JJ

@@

After this process, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions as they provide information, while others may not be 
necessary and even redundant.

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Additionally, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

@@

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
It is a very useful analysis tool for visualising complex data with
high number of variables in a simple geometric plane. Therefore, it
could be used for different tasks such as feature selection and data
clustering and visualisation. %Pablo: some cite here?

@@

SOM follows an iterative process applied in two stages: First, the
weights of the network are initialized randomly, then the n-dimensional
input vectors are presented to the network sequentially so the
distance between the weights of the neurons and the inputs are
computed using the simple Euclidean distance; in the second stage, the
neuron which has the shortest distance with the presented input vector
is updated along with its neighbor neurons. This neuron is called the
best matching unit (BMU). The goal of the learning process is to
minimize the neighborhood distance in the output clusters.

When the learning process is done a visual representation method like
the Unified Distance Matrix, or U-matrix for short, is used to
visualize the distances between neurons in the output space. In the
U-matrix, the distance between adjacent neurons is measured and
assigned different colors. Dark colors between neurons indicate large
distances (boundaries) while ligh colors represent similar areas
(clusters).

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions, or clusters, with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ

@@

\begin{table}
\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation. Best values in bold.
\label{tab:all_publishers_no_fs}}
\centering{}%
\scalebox{0.78}{

\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  &  \textbf{89.0 $\pm$ 0.09}  &  \textbf{214.37 $\pm$ 22.96}  &  \textbf{634.23 $\pm$ 307.76}  &  \textbf{37.46 $\pm$ 3.12}  &  \textbf{48.32 $\pm$ 25.16} & 18.85 $\pm$ 0.61\tabularnewline
\hline 
K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  &  \textbf{0.001 $\pm$ 0.01}\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

After applying the feature selection methods, we have run the same forecasting models as in Section \ref{subsec:results_all_publishers} for the whole dataset (all the publishers), but considering only the selected features by each method. The results are shown in Table \ref{tab:results_all_publishers_fs}. Examining the obtained results for each feature selection method, it can be seen that RFE got the best results compared to SOM and CSE. It can be noticed also that the performance of M5P, kNN and RF has been improved with RFE compared to the case of using all features. In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values. On the other side, CSE and SOM did not perform as good as RAE which could be explained due to the extensive reduction made by CSE and due to the human intervention in the case of SOM.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of how
many books should be printed for delivery to bookstores; printing too
many is the main issue, since it implies a loss of investment due to
inventory excess, but printing too few will also have a negative economical impact. In this paper, we are tackling the problem of predicting total sales in order to print the right amount of books and doing so even before the book has reached the stores. A real dataset including the complete sales data for books published in Spain across several years has been used.
We have conducted an analysis in three stages: an initial exploratory analysis, by means of data visualisation techniques; a feature selection process, using different techniques to find out what are the variables that have more impact on sales; and a regression or prediction stage, in which a set of machine learning methods have been applied to create forecasting models for book sales. 
The obtained models are able to predict sales from pre-publication data with
remarkable accuracy, and can be visualised as simple decision trees. Thus, these can be used as decision-aid tools for publishers, which can provide a reliable guidance on the decision process of publishing a book. 
This is also shown in the paper by addressing four example cases of representative publishers, regarding their number of sales and the number of different books they sell.
\end{abstract}

@@

Publishing a book, in the same way as releasing any other cultural product with a physical substrate, implies several types of risks and costs due to
the complexity, and derived expenses, of the production,
distribution, and storage processes; most of these costs are associated
to the number of books actually printed. But the problem is further
complicated for completely new products, in the sense that there is an unknown
author or a new topic with no track record. Sales forecasts can
only be based on the knowledge obtained from other similar products,
but the definition of ``similar'' itself is fuzzy and, sometimes,
subjective. Even if the author or the topic is known, doing accurate
estimations of future sales of the new product is quite difficult, and extremely important, so that production runs heed predicted sales. 
Indeed,several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
production process \cite{Fildes2010,Saeed2008}.

@@

Specifically, time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}  
is perhaps the most used technique to tackle the sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this paper.

@@

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production, i.e. how many books should be printed when a new
book is published. 
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analysing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

In order to deal with this issue, i.e. forecasting sales of new products, some authors have used different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
% Antonio - Maybe we should describe them briefly...
%
In the same line, Thomassey et al. \cite{SThomassey2014} propose using a clustering method together with decision trees for sales forecasting in textile-apparel fashion industry, 
a very similar issue to the new book publishing one.
The same problem was previously faced by Xia et al. \cite{Xia2012} using a 
forecasting method based on extreme machine learning with adaptive metrics of inputs.
% Antonio - of -> as???
The complexity of this problem relies on the lack of historical data, on the short lifetime of the majority of items, 
% Antonio - ver si está bien el cambio 'large number' -> 'majority'
and on the influence of variables such as promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}, as mentioned above.
%FERGU: completar con: "In our case, these ideas ..."

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again? - JJ
                   % No, above we said that the efficiency depends on the field 
                   % of application and the available problem data. - pedro
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. 
The proposed method is suitable for those sales forecasting problems 
with a big amount of online reviews and historical data.

@@

The main objective of this paper is to forecast sales for 
%FERGU: el objetivo es la herramienta o la predicción?
unpublished books for which no historical data are available. Instead, just some
%FERGU: pero usamos datos históricos de otros para la predicción, no? Como otros papers...
descriptive and variables known in advance related to the new book. In
order to do that, we have used a training dataset which includes
historical sales data for a big amount of books published in Spain for
several years, with a set of 50 features or variables per pattern.

@@

In this prediction problem there are other external variables that also affect 
the sales of a new book, such as those related to seasonality, trends or 
promotions, that classical prediction methods can not deal with. %FERGU: por qué?
However, an expert can consider them to modify the forecast obtained by 
the automatic method. Even publishing companies tend to define rules or 
indexes to subjectively adjust the results of prediction based on
external data. 
Thus, the proposed method, will analyse the provided data and
variables and will yield a forecast of sales according to them. This
result could be used as a reference for a human expert, who would
consider it in his/her own prediction process.

@@

First, after the publishing company has provided the raw data
(extracted directly from its database), a preprocessing method has
% This should go to the previous section. 
been performed in order to remove incorrect or incoherent patterns,
such as those with null values in required variables, or with negative
sales, for instance. Moreover, the initial set of variables (presented
in Table \ref{tabla:paramsOrig50}) has been reduced by an expert to
use just those that can be known in advance when a new book is
launched, i.e. \textit{pre-sales data}.

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
Then, a Feature Selection (FS) process \cite{kittler1986feature} has
been carried out, as it is an effective dimensionality reduction
technique and an essential preprocessing method to discard `noisy'
(non-useful) features \cite{Krishnapuram2004}. The aim of these
% Did you know there were noisy features? Why? 
% You should include in the previous section an exploratory data
% analysis that describes the range of variables, how many categories
% those variables have, and so an do forth - JJ 
algorithms is exploring the space of attributes to find out which
subset of them yields the best results in a classification or
prediction problem. 
  In this stage, both, numerical and visualisation-based approaches have been applied in this paper, in order to select the best variables for the forecasting 
methods.  
% Antonio - Decidir si es 'forecasting' o 'regression' (o si son indiferentes) y usarlo siempre en el texto
  This task may also help to identify leading indicators to be considered by a human expert to make predictions.

@@

Once the models and results have been obtained for the whole dataset, the same methodology has been applied to some specific cases (publishing companies) in order to prove the value of the proposal.
Some specific interpretable models have been created as a final result of the work. The aim is that these will cold be used as a decision-aid tool for the experts who have to take decide about the best print-run quantity for new published books, in order to, logically maximise the benefit (or minimise the costs).

@@

In general, historical data are used to make time series, and from them extracting common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010}. Thus, only pre-sales data are available in this problem.

Moreover, the initial set of features in the dataset must be revised in order to consider just those that can be known before the launch of the book, i.e. those whose value don't depend on the book sales. So, we have selected the subset of features described in Table \ref{tabla:params_pre_sales}.

\begin{table}
% Shouldn't this table go to "Problem description"? It is a
% preliminary selection - JJ
\caption{Considered pre-sales features and their types. It also shows
  the names of the variables used in the applied methods and if everyone is an input (independent) or an output (dependent) variable.} 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 &  publisher + collection (joint code) & \texttt{collection} & categorical & input\\
4 & bookbinding (code) & \texttt{binding} & categorical & input\\
5 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
6 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
7 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
8 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
9 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
10 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
11 & total sales & \texttt{total\_sales} & numerical & output\\
\hline 
\end{tabular}
\end{center}
\end{table}

As it can be seen in the table, \texttt{total\_sales} is the output variable, so it is the objective of the prediction methods. \texttt{print\_run} has been considered as an input variable because it is something to be decided in advance by a publisher. In addition, this variable could be interesting to be used to test the prediction model, once it is built. So the publisher could try different values for it and see what the predictor yields, in order to take the best decision.

@@

Regarding the feature \textit{publisher}, we have removed it from the final dataset since it is indeed included in the code of \texttt{collection}. In addition, we think it is not really relevant for the accuracy of the models and, moreover, publishers will not consider the results in other publishing companies for predicting its own sales.
% Antonio - Think about this... should we mention this?

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

@@

Once a dataset has been composed it must be preprocessed, i.e. it
should be revised in order to fix the existing errors (such as wrong
or duplicated patterns), or to complete (or address) the absence of
information, for instance. The aim is looking for the correctness,
homogeneity and completeness of the data. % useless paragraph - JJ

@@

After this, the features describing every pattern are frequently analysed.
In this case, among the variables describing a new book, some may affect 
predictions (those variables provide information), while others may not be 
necessary and even redundant.

% You have to justify its application to this particular problem. What
% was the runnning time with all variables? What reduction was your
% target? - JJ
Moreover, the algorithm running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}. Feature reduction is a task that is usually
applied in these kind of situations, having two ways of performance
\cite{kittler1986feature}: feature extraction and feature selection.  
% two ways of performance? WTF? Do you mean "being performed in two
% different ways?" - JJ
%Feature selection task is usually carried out by 
%searching through all possible combinations of features, evaluating each one.

@@

SOM is a type of unsupervised neural network inspired by the
topographical organisation of the sensory cortex of human brain
\cite{kohonen1998}. It maps highly dimensional data into a lower
dimensional space where similar data patterns are located in more
adjacent areas on the grid. 
It is a very useful analysis tool for visualising complex data with
high number of variables in a simple geometric plane. Therefore, it
could be used for different tasks such as feature selection and data
clustering and visualisation.

@@

SOM follows an iterative process applied in two stages: First, the
weights of the network are initialized randomly then the n-dimensional
input vectors are presented to the network sequentially so the
distance between the weights of the neurons and the inputs are
computed using the simple Euclidean distance; in the second stage, the
neuron which has the shortest distance with the presented input vector
is updated along with its neighbor neurons. This neuron is called the
best matching unit (BMU). The goal of the learning process is to
minimize the neighborhood distance in the output clusters.

When the learning process is done a visual representation method like
the Unified Distance Matrix, or U-matrix for short, is used to
visualize the distances between neurons in the output space. In the
U-matrix, the distance between adjacent neurons is measured and
assigned different colors. Dark colors between neurons indicate large
distances (boundaries) while light colors represent similar areas
(clusters).

@@

This method is usually applied to analyse data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those
regions (clusters) with high training sample concentration and fewer
where the samples are scarce.  
%FERGU: mencionarlo en la intro
% Which is interesting because... JJ

@@

\begin{table}
\caption{Predicting Total sales for all publishers (all the features). 10 repetitions, 10-fold cross validation.
\label{tab:all_publishers_no_fs}}
\centering{}%
\scalebox{0.85}{

\begin{tabular}{|c|l|l|l|l|l|l|}
\hline 
 & $R^{2}$  & MAE  & RMSE  & RAE (\%)  & RRSE (\%)  & Time (s)\tabularnewline
\hline 
M5P  & 89.0 $\pm$ 0.09  & 214.37 $\pm$ 22.96  & 634.23 $\pm$ 307.76  & 37.46 $\pm$ 3.12  & 48.32 $\pm$ 25.16  & 18.85 $\pm$ 0.61\tabularnewline
\hline 
K-NN  & 78.7 $\pm$ 0.08  & 272.29 $\pm$ 32.38  & 840.59 $\pm$ 240.11  & 47.48 $\pm$ 3.39  & 63.07 $\pm$ 10.29  & 0.001 $\pm$ 0.01\tabularnewline
\hline 
RF & 84.0 $\pm$ 0.05  & 253.37 $\pm$ 29.43  & 788.94 $\pm$ 282.01  & 44.16 $\pm$ 2.76  & 57.77 $\pm$ 8.15  & 4.91 $\pm$ 0.12\tabularnewline
\hline 
LR & 87.2 $\pm$ 0.07  & 308.68 $\pm$ 25.44  & 680.91 $\pm$ 226.41  & 54.05 $\pm$ 4.38  & 52.13 $\pm$ 18.29  & 984.68 $\pm$ 128.21\tabularnewline
\hline 
SVM  & 87.6 $\pm$ 0.04  & 248.76 $\pm$ 27.49  & 732.64 $\pm$ 260.56  & 43.37 $\pm$ 2.35  & 53.47 $\pm$ 6.29  & 6169.24 $\pm$ 281.49\tabularnewline
\hline 
\end{tabular}
}
\end{table}

@@

After applying the feature selection methods, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. The results are shown in Table
\ref{tab:results_all_publishers_fs}. Examining the obtained results
for each feature selection method, it can be seen that RFE got the
best results compared to SOM and CSE. It can be noticed also that we
obtain better performance in M5P, kNN and RF using only features
selected by RFE than using all features. %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
 In general, all feature selection methods have reduced the training time needed to build the forecasting methods, this is because they reduced the features and excluded the categorical features that have many possible values. On the other side, CSE and SOM did not perform as good as RAE which could be explained due to the extensive reduction made by CSE and due to the human intervention in the case of SOM.
